An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
some revisions to building/testing

CloudCoder currently supports exercises for C/C++, Java, Python and
Ruby.  Building and testing takes place in a separate process which
can be run on a separate machine for extra security, or on multiple
machines for scalability.

We run Java code relatively securely under a Security Manager, and 
use Jython\cite{jython} and JRuby\cite{jruby} to compile Python and Ruby to Java
bytecode, which we also run in a Security-Managed sandbox.  We
currently support C/C++ less securely, although 
we hope to take advantage of a better sandboxing mechanism
in the near future, possibly based on the work of
David Malan\cite{Malan:2013:CSS:2445196.2445242} for Harvard's
online CS50 course.

>>>>

CloudCoder currently supports exercises for C/C++, Java, Python and
Ruby.  Building and testing takes place in a separate process which
can be run on a separate machine for extra security, and on multiple
machines for scalability.

CloudCoder executes Java, Python, and Ruby code relatively securely under
a Java Security Manager.
(CloudCoder uses Jython\cite{jython} and JRuby\cite{jruby}
to execute Python and Ruby submissions, allowing us to take advantage of
the Java Security Manager for those languages.)
CloudCoder's execution of C/C++ code is somewhat less secure, although 
we hope to take advantage of a better sandboxing mechanism
in the near future, possibly based on the work of
David Malan\cite{Malan:2013:CSS:2445196.2445242} for Harvard's
online CS50 course.  However, because thus far the only users of
CloudCoder have been instructors and students in introductory courses,
the weak sandboxing has not been a significant concern.
